Katana: Towards Patching as a Part of the ELF Toolchain

### 2010-03-18 paper1/hotpatch/conclusion.tex
changed hyphenation of multithreading to be consistent

We present a reasoned approach to making patching a part of the
standard tool chain. We demonstrate a working binary userland patcher
operating completely at the object level. Our system is, to our
knowledge, the first to utilize DWARF type information to automate the
transformation between old and new versions of a type. There yet
remains much work to be done, and our future work involves support for
patching multi-threaded targets, better support for handling opaque
types such as \texttt{void}*, and further development of patch
versioning and the ability to perform operations on patch objects.

>>>>

We present a reasoned approach to making patching a part of the
standard tool chain. We demonstrate a working binary userland patcher
operating completely at the object level. Our system is, to our
knowledge, the first to utilize DWARF type information to automate the
transformation between old and new versions of a type. There yet
remains much work to be done, and our future work involves support for
patching multithreaded targets, better support for handling opaque
types such as \texttt{void}*, and further development of patch
versioning and the ability to perform operations on patch objects.
